Lasso_RCI_Response

### 2024-02-18 Lasso_RCI_Response.Rmd
I DID THE THING!!!

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

@@

```{r}
# 1. Re-coding / Renaming variables ------------------------------------------
# We can change the current variables to make them easier to interpret.
str(Mothership_post$Education_1)

@@

                                          "<Grade 12" = "No College",
                                          "<Grade 12" = "No College",
                                          "HS Diploma or GED" = "No College",
                                          "HS Diploma or GED" = "No College",
                                          "Some College/Associates Degree" = "Some College",
                                          "Some College/Associates Degree" = "Some College",
                                          "Bachelors Degree" = "Some College",
                                          "Bachelors Degree" = "Some College",
                                          "Grad Degree" ="Some College"),

@@

                                       "Female" = "Female",
                                       "Male" = "Not",
                                       "Non-Binary" = "Not",
                                       "Other" = "Not",
                                       "Other" = "Not"),

@@

                                             "Married or Cohabitating" = "Married or Cohabitating",
                                             "Widowed or Separated" = "Not",
                                             "Divorced" = "Not",
                                             "Single or Never Married" = "Not"),

@@

                                         "Straight" = "Straight",
                                          "Gay" = "Not Straight",
                                          "Bisexual" = "Not Straight",
                                          "Other" = "Not Straight"),

@@

                                     "White" = "White",
                                     "Black" = "Not White",
                                     "Hispanic"="Not White",
                                     "Asian"="Not White",
                                     "Portugese"="Not White",
                                     "Other"="Not White"),

@@

                                          "Treatment Complete" = "Treatment Successful",
                                          "Treatment nearly complete" = "Treatment Successful",
                                          "Insurance no longer covering" = "Other",
                                          "Nonattendance" = "Other",
                                          "Inappropriate (language)/Referred to another tx setting" ="Other",
                                          "Transferred to inpatient"="Other",
                                          "Withdrew due to external limitations"="Other",
                                          "Withdrew AMA"="Other",
                                          "Other"="Other",
                                          "Other"="Other",
                                          "Other"="Other"),

@@

          Social_P == 1 | Specific_P == 1, 1, 0)),

@@

    OCD_P = as.factor(OCD_P),

@@

          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | Schiz_P == 1 | 
          Schizaff_P == 1 | Alcohol_P == 1 | Drug_P ==1 | OCD_P ==1,

@@

             ifelse(OCD_P == 1, "OCD",

@@

                                                              )))))))))),

@@

                                  ifelse(OCD_P == 1, "Other",

@@

                                                       ifelse(Eating_D == 1, "Other", NA

@@

@@

    OCD_Co_C = as.factor(
      ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
    BPD_Co_C = as.factor(
      ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
    No_Co = as.factor(
      ifelse(BPD_Co_C == 0 &
               OCD_Co_C == 0 &
               Somatic_C == 0 & 
               Eating_C == 0 &
               Psychotic_C == 0 &
               Trauma_C == 0 & 
               Substance_C == 0 &
               Mood_C == 0 &
               Anxiety_C == 0, 1,0)),
    Other_Co = as.factor(
      ifelse(OCD_Co_C == 1 & 
               Somatic_C == 1 & 
               Eating_C == 1 &
               Psychotic_C == 1,1,0)),

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & OCD_P == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & OCD_P == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_OCD = as.factor(
      ifelse(OCD_C == 1 & Anxiety_D == 1 |
               OCD_C == 1 & Mood_D == 1 |
               OCD_C == 1 & BPD_P== 1 |
               OCD_C == 1 & Substance_D == 1 |
               OCD_C == 1 & Trauma_D == 1 |
               OCD_C == 1 & Eating_D ==1 |
               OCD_C == 1 & Psychotic_D ==1 |
               OCD_C == 1 & Somatic_D ==1, 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_C == 1 & Anxiety_D == 1 |
               BPD_C == 1 & Mood_D == 1 |
               BPD_C == 1 & OCD_P== 1 |
               BPD_C == 1 & Substance_D == 1 |
               BPD_C == 1 & Trauma_D == 1 |
               BPD_C == 1 & Eating_D ==1 |
               BPD_C == 1 & Psychotic_D ==1 |
               BPD_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & OCD_P == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & OCD_P == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & OCD_P == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & OCD_P == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & OCD_P == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
  )

##### df for plots

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
  filter(
    is.na(Prev_AdmitID_1),
    C_Admit_1 == 1
  ) |>
  mutate(
    dummy = -99
  )

# df without NAs in date and disorder type
Mothership_Diag <- Mothership |>
  filter(!is.na(Disorder_Type)) |>
  filter(!is.na(TxYear))

# Mothership_Diag_treat <- Mothership |>
#   filter(!is.na(Disorder_treat),
#          !is.na(TxYear),
#          !is.na(Duration))

### Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")

@@

#1. load DF
  Mothership_post <- Mothership_Diag_treat

@@

RCI_DF

###############          Adding RCI to dataset       ####################

@@

## Part 1: Who is attending?

@@

#Full demographic break down
co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat))

@@

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
cor_tab<- Mothership_post |>
  select( c(
    # Demographics
    Age_1,Some_College:Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, # Days_noshow_1, Days_not_attended_1, Days_cancel_1,
    # Disorders
    Mood_D:Other,Co_Anx:Co_Trauma,Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_sym_change

  ))

#comments about what I should do
      #Should I make a level of anxiety / depression - cuxos cut offs?
      # should I use the first score or the pre score?
      # Should I do each individual disorder, or just the overarching classes (i.e., depression)?
      # should I include co_occuring even if there is a lot of overlap (i.e., depressive P and Co)

# View(cor_tab)
# View(Mothership_post)

# install.packages("ggcorrplot")
# library(ggcorrplot)
model.matrix(~0+., data=cor_tab) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}
DEP_RCI <- JTRCI (data = RCI_df_dep, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "RCI", 
                  #JTcrit = "auto",
                  plottitle = "Anxeity: JT indices by disorder")

RCI_DF

###############          Adding RCI to dataset       ####################

@@

\scriptsize
```{r, warning=FALSE, message=FALSE}
library(glmnet)
ecls2$preds = as.matrix(ecls2[ ,c(1:8,14:22)])

# lambda = 0
lasso1 = glmnet(ecls2$preds, ecls2$g8_sci_tht, alpha=1, lambda=0, 
                standardize=TRUE, intercept=TRUE)
lasso1

coef(lasso1)
```

### Lasso Regression
\scriptsize
```{r}
## lambda = .1
lasso2 = glmnet(ecls2$preds, ecls2$g8_sci_tht, alpha=1, lambda=.1,
                standardize=TRUE, intercept=TRUE)
lasso2

coef(lasso2)
```

### $k$-fold Cross Validation
\scriptsize
```{r, warning=FALSE, message=FALSE}
#1. set seed
set.seed(19860608)
#2. sample data from the number of rows in els2
ecls2 = ecls2[sample(nrow(ecls2)),]
#3. convert ecls2a a new datafraame that is scaled and mean centered.
ecls2a = as.data.frame(scale(ecls2, center=TRUE, scale=TRUE))
#4. create a new column of values with predictors
ecls2a$pred = as.matrix(ecls2a[,c(1:8,14:22)])

#5. define the number of folds: cut a sequence from 1-num rows in ecls2a, broken into 10 equal parts, without labels)
folds = cut(seq(1,nrow(ecls2a)), breaks=10, labels=FALSE)

#6. create a grid (Sequence) from 0 - 1 increasing by .001
grid = seq(0, 1, by=.001)
#.7 make a matrix full of NAs that is 10 columns wide and the length of grid long? 
    # I think MSE = mean squared error?
mse  = matrix(NA, 10, length(grid))

#8. create a for loop (for each row in the number of columns (1-10))
for(i in 1:10){
  #9. the test cases are the first number for each fold
  testCases = which(folds==i,arr.ind=TRUE)
  test      = ecls2a[testCases, ]
  #10. the train cases are the valeus not the test cases
  train     = ecls2a[-testCases, ]

  #11. another for loop for each value in 1 - length of grid)
  for (j in 1:length(grid)){
    #12. k lambda = the index of grid[j]
    klambda = grid[j]
    #13. run a fit train regression model with predictors, for train$g8_Sci_tht.
    fitTrain = glmnet(train$pred, train$g8_sci_tht, 
                      alpha=1, lambda=klambda,
                      standardize=FALSE, intercept=TRUE)
    #14. predict the test values using predict using the fitTrain model, and using the new x values as test$pred
    fit_test = predict(fitTrain, newx=test$pred)
    #15. at each index of mse, take the mean of the differnece between the test value, and the fit test values and square them
    mse[i,j] = mean((test$g8_sci_tht - fit_test)^2)
  }
}

# 16. load matrixStats
library(matrixStats)

#17. assign a varaible that is column means of mse
mseMeans = colMeans(mse, na.rm=TRUE)
#18. assign column sd
mseSds = colSds(mse, na.rm=TRUE)

# Find minimum - find the one which has the minimum mean square error 
best = which.min(mseMeans)
grid[best]

# Find simplest model within 1 Standard Error - best close 
maxMse = mseMeans[best] + mseSds[best]/sqrt(10)
bestClose = max(which(mseMeans<maxMse))
grid[bestClose]
```

K-fold cross-validation can be performed using the cv.glmnet function. In addition to all the glmnet parameters, cv.glmnet has its special parameters including nfolds (the number of folds), foldid (user-supplied folds), and type.measure(the loss used for cross-validation):

“deviance” or “mse” for squared loss, MSE = mean squared loss

### Lasso Regression
\scriptsize
```{r}
lasso3 = glmnet(ecls2a$pred, ecls2a$g8_sci_tht, alpha=1, lambda=grid[best],
                standardize=FALSE, intercept=TRUE)
coef(lasso3)
```

### Lasso Regression
\scriptsize
```{r}
lasso4 = glmnet(ecls2a$pred, ecls2a$g8_sci_tht, alpha=1, lambda=grid[bestClose],
                standardize=FALSE, intercept=TRUE)
coef(lasso4)
```

### Relaxed Lasso
\scriptsize
```{r}
rlasso4 = lm(g8_sci_tht~gender+kage+k_math_tht+k_gk_tht+f_mtr+
             poor, data=ecls2)
summary(rlasso4)
```

*Relaxed Lasso*
- I After variable selection using the lasso, an OLS regression model is fit with only the variables selected
- The estimates for retained variables are not shrunken

*Cautions*
- When performing cross validation, it’s important to standardize
variables before creating folds
- Similarly, when creating the final prediction model, it is important for the standardization process to be the same across datasets
    + Same means and standard deviations are used across datasets
- Relaxed lasso avoids the standardization process when creating
final model
- Built in k-fold cross-validation using glmnet:

### $\mathtt{cv.glmnet}$ function in $\mathtt{glmnet}$
 - Built in $k$-fold cross-validation using $\text{glmnet}$

\scriptsize
```{r}
cvGlmnet = cv.glmnet(ecls2a$pred, ecls2a$g8_sci_tht, 
                     alpha=1, type.measure='mse', 
                     nfolds=10)
cvGlmnet$lambda.min
cvGlmnet$lambda.1se

plot(cvGlmnet)
```

>>>>

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

@@

```{r}
# 1. Re-coding / Renaming variables ------------------------------------------
# We can change the current variables to make them easier to interpret.

@@

                                          "<Grade 12" = "0",
                                          "<Grade 12" = "0",
                                          "HS Diploma or GED" = "0",
                                          "HS Diploma or GED" = "0",
                                          "Some College/Associates Degree" = "1",
                                          "Some College/Associates Degree" = "1",
                                          "Bachelors Degree" = "1",
                                          "Bachelors Degree" = "1",
                                          "Grad Degree" ="1"),

@@

                                       "Female" = "1",
                                       "Male" = "0",
                                       "Non-Binary" = "0",
                                       "Other" = "0",
                                       "Other" = "0"),

@@

                                             "Married or Cohabitating" = "1",
                                             "Widowed or Separated" = "0",
                                             "Divorced" = "0",
                                             "Single or Never Married" = "0"),

@@

                                         "Straight" = "1",
                                          "Gay" = "0",
                                          "Bisexual" = "0",
                                          "Other" = "0"),

@@

                                     "White" = "1",
                                     "Black" = "0",
                                     "Hispanic"="0",
                                     "Asian"="0",
                                     "Portugese"="0",
                                     "Other"="0"),

@@

                                          "Treatment Complete" = "1",
                                          "Treatment nearly complete" = "1",
                                          "Insurance no longer covering" = "0",
                                          "Nonattendance" = "0",
                                          "Inappropriate (language)/Referred to another tx setting" ="0",
                                          "Transferred to inpatient"="0",
                                          "Withdrew due to external limitations"="0",
                                          "Withdrew AMA"="0",
                                          "Other"="0",
                                          "Other"="0",
                                          "Other"="0"),

@@

          Social_P == 1 | Specific_P == 1 | OCD_P == 1, 1, 0)),

@@

        #OCD_P = as.factor(OCD_P),

@@

          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | 
          Schiz_P == 1 |  Schizaff_P == 1,  

@@

@@

@@

                                  #ifelse(OCD_P == 1, "Anxiety",
                                     #felse(OCD_P == 1, "Other",

@@

                                                       ifelse(Eating_D == 1, "Other",
                                                          ifelse(Somatic_D == 1, "Other",NA

@@

                #OCD_P != 1 & OCD_C == 1 |

@@

    Other_C = as.factor(
        Somatic_C == 1 | Eating_C == 1 | Psychotic_C == 1, 1, 0)),

    #OCD_Co_C = as.factor(
     # ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
    BPD_Co_C = as.factor(
      ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
    No_Co = as.factor(
      ifelse(BPD_Co_C == 0 &
               Somatic_C == 0 & 
               Eating_C == 0 &
               Psychotic_C == 0 &
               Trauma_C == 0 & 
               Substance_C == 0 &
               Mood_C == 0 &
               Anxiety_C == 0, 1,0)),
    Other_Co = as.factor(
      ifelse(  Somatic_C == 1 & 
               Eating_C == 1 &
               Psychotic_C == 1,1,0)),

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )

summary(Mothership$Co_Anx)
table(Mothership$Anxiety_D, Mothership$Co_Anx)
##### df for plots

# only include people that attend treatment & its thier first time attending
Mothership <- Mothership |>
  filter(
    is.na(Prev_AdmitID_1),
    C_Admit_1 == 1
  ) |>
  mutate(
    dummy = -99
  ) |>
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

# df without NAs in date and disorder type

Mothership_Diag_treat <- Mothership |>
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

### Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag_treat.csv")

@@

#1. load DF
  Mothership_post <- Mothership

@@

RCI_DF
```

```{r}
###############          Adding RCI to dataset       ####################

@@

# Data analysis 
## Part 1: Who is attending?

@@

#Full demographic break down

co_dis_tab <- Mothership_post |>
  filter(
      !is.na(rdq_func_change),
      !is.na(rdq_pmh_change),
      !is.na(rdq_coping_change),
      !is.na(rdq_wbs_change)
  ) |>
  pivot_longer(
    cols = c("Anxiety_C","Mood_C","BPD_Co_C","Other_C", "Substance_C","Trauma_C", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat),
         )

@@

- Table 3: Correlation table?
- supplemental table 1: Full diagnostic breakdown of sample 
  + (co-occuring by Disorder)
```{r}
Vars_FULL <- Mothership_lasso |>
  select( c(
    RESPONDER_FIGS,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))
Vars_FULL <- na.omit(Vars_FULL)

# install.packages("ggcorrplot")
library(ggcorrplot)
model.matrix(~0+., data=Vars_FULL) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
```

## Part 2: RCI ANALYSIS - Treatment Response
Anxiety & Depression = Total response
- Table 4: RCI Analsyis results
  + Anxiety, Depression, Total response
- Figure 2 / Supplimetal 2: RCI Analysis figs 
  + Anxeity & Depression
```{r}

RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
#anxiety 
RCI_table[1,] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
# Depresssion
RCI_table[2,] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
#Total
RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])

RCI_table
```

@@

https://github.com/sydeaka/Using-Elastic-net-for-model-Selection-with-missing-data/blob/master/model_selection_missing_data-example.R
http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/

Preparing data for Lasso
\scriptsize
```{r, warning=FALSE, message=FALSE}
library(glmnet)
library(caret)
#Make sure there are no NAs within the dataset
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(RESPONDER_FIGS)
  )

# View(Mothership_lasso)

Vars <- Mothership_lasso |>
  select( c(
    RESPONDER_FIGS,
    # Demographics
    Age_1,Some_College:Married,White,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, 
  ))

```{r, warning=FALSE, message=FALSE}
# View(Mothership_lasso)
# head(Vars)
# sum(is.na(Vars))
Vars_FULL <- Mothership_lasso |>
  select( c(
    RESPONDER_FIGS,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_FULL <- na.omit(Vars_FULL)
```
# with RDQ
```{r}
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_FULL$RESPONDER_FIGS %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars_FULL[training.samples, ]
test.data <- Vars_FULL[-training.samples, ]

# Dumy code categorical predictor variables
x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)

#Simplified lasso
lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
plot(lasso1, "lambda", label = TRUE)
```

Find coefficients using cv.lasso
```{r}
# Find the best lambda using cross-validation
set.seed(123) 
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")

#The exact value of lambda can be viewed as follow:
print(paste0("This is the minimum lambda value: ", round(cv.lasso$lambda.min,5)))

#This value is called lambda.1se.
print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso$lambda.1se,5)))

# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
mean(predicted.classes == observed.classes)

#Using lambda.min as the best lambda, gives the following regression coefficients:
coef(cv.lasso, cv.lasso$lambda.min)

#Using lambda.1se as the best lambda, gives the following regression coefficients:
coef(cv.lasso, cv.lasso$lambda.1se)
```

Evaluating if we should use Lasso min or 1SE
```{r}
####  Using Min
# Final model with lambda.min
lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.min)

coef(lasso.model.min)
# Make prediction on test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- lasso.model.min %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
Mean.predict.min <- mean(predicted.classes == observed.classes)

#####  using 1se
# Final model with lambda.1se
lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
                      lambda = cv.lasso$lambda.1se)
coef(lasso.model.1se)
# Make prediction on test data
x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
probabilities <- lasso.model.1se %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")

# Model accuracy rate
observed.classes <- test.data$RESPONDER_FIGS
Mean.predict.1se <- mean(predicted.classes == observed.classes)

#### full model
# Fit the model
full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$RESPONDER_FIGS
Mean.predict.full.model <- mean(predicted.classes == observed.classes)

predict.df <- data.frame(
  model = c("Min", "1se", "Full"),
  values = c(Mean.predict.min,Mean.predict.1se,Mean.predict.full.model)
)
predict.df
```
plot the lassos
If We want to do lasso in ggplot
https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients

```{r}
##plot the lambda
plot(lasso1, "lambda", label = TRUE)
## Fancy plot
library(lars)
lasso_FULL = lars(x, y, type='lasso', 
              trace=TRUE, normalize=FALSE, intercept=TRUE)
plot(lasso_FULL, xvar='norm', breaks = FALSE, 
     plottype = 'coefficients', omit.zeros = TRUE)

#CV k folds cross validation
plot(cv.lasso)
```

### Final relaxed lasso
Minimum
```{r}
## install.packages("fuzzySim")
library(fuzzySim) ## For FDR adjusted p values
FDR(pvalues = p_values.min)

library(broom)
# https://cran.r-project.org/web/packages/broom/vignettes/broom.html

## min model
  glm_min <-  
      glm(
      #Outcome varaible
        RESPONDER_FIGS ~ 
      # predictors
        Days_not_attended_1 + Anxiety_D + Mood_D + Substance_C + 
        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
      #data
      data = Vars_FULL, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.min      <- summary(glm_min)

  tidy.summary.min <- tidy(glm_min)

# Coefficients
  coefs.min <- abs(coef(glm_min))

# Odds ratio
  OR.min <- exp(coef(glm_min))

# OR 95% CI
  CI.min <- data.frame(exp(confint(glm_min)))

# P values
  p.values.min <- data.frame(cbind(tidy.summary.min$term,tidy.summary.min$p.value))
  # FDR Adjusted P Values
    adj.p.min <- FDR(pvalues = p_values.min)
    ADJ.p.values.min <- data.frame(rbind(adj.p.min$exclude, adj.p.min$select))

# R^2 values  
   R2.min <- performance::r2(glm_min)

# df for Forrest plots
FP.min <- data.frame(cbind(
  Variable = tidy.summary.min$term[2:length(tidy.summary.min$term)],
  OR = OR.min[2:length(OR.min)],
  OR_low  = CI.min[2:length(CI.min$X2.5..),1],
  OR_high = CI.min[2:length(CI.min$X97.5..),2],
  p.values = p.values.min$X2[2:length(p.values.min$X2)]
                    ))

# Left join the FDR adjusted p.value
FP.min <- left_join(FP.min,ADJ.p.values.min, by = join_by(p.values == p.value))
FP.min
```
